DRAFT \\ From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics

### 2016-09-30 2015CompleteDerivation/completeDerivation.tex
Comments from Jiahua

We claim $\mathcal{T}_{\Delta t}$ is continuous. Let $U \subseteq \mathcal{S}$ represent an outcome of a process $P$ on the final states. $U$ is an open set in the (final) state space topology by definition. Consider the process $P_0$ that evolves the initial states and then distinguishes the final state with $P$. $P_0$ is a process that distinguishes initial states. The set of initial states compatible with $U$ are $\mathcal{T}_{\Delta t}^{-1}(U)$. $\mathcal{T}_{\Delta t}^{-1}(U)$ is an open set in the (initial) state space topology by definition. $\mathcal{T}_{\Delta t}$ is a continuous map.

@@

\begin{justification}
	Same justification for continuity as in \ref{detrevmap} with "initial states" and "final states" replaced by "elements" of $\mathcal{S_1}$ and $\mathcal{S_2}$ respectively.
\end{justification}

@@

When combining multiple state variables, it is important to understand how they relate to each other. Consider the orbital of an electron in a hydrogen atom, which is identified by the quantum numbers $n$, $l$, $m$ and $s$. For each combination of $n$, $l$ and $m$, the spin $s$ can have two values. The choice of spin is independent from the rest. The choice of $l$, though, depends on the choice of $n$: for $n=1$ only $l=s$ is available; for $n=2$ we can choose $l=s$ or $l=p$. The choices are not independent. That is: two or more variables are independent if there always exists a state for any possible combination, if the total number of states is the cartesian product of the possibilities of each variable. We call \emph{state vector} a collection of independent state variables that fully identify a state.

\begin{prop}\label{independent_state_variables}
	Two state variables $q_1 : U \rightarrow \mathbbm{L}_1$ and $q_2 : U \rightarrow \mathbbm{L}_2$ are said \emph{independent} if $\exists \mathcal{s} | q_1(\mathcal{s})=l_1, q_2(\mathcal{s})=l_2 \forall l_1 \in q_1(U), l_2 \in q_2(U)$.
\end{prop}

@@

We will call a \emph{classical material} one that is homogeneous and infinitesimally reducible. That is, we can keep decomposing the system indefinitely into smaller and smaller parts, each with a well defined state. In this case, the particles are the infinitesimal parts given by the limit of this process of recursive decomposition. Giving the state of the whole system is equivalent to giving the states of all particles. Given the state space $\mathcal{S}$ for the infinitesimal parts, which we assume to be a manifold consistently with \ref{continuous_state_space}, a composite state $\mathcal{c} \in \mathcal{C}$ will tell us the amount of material for each possible particle state. That is, each state is fully identified by a function $\rho_\mathcal{c}: \mathcal{S} \to \mathbbm{R}$ that returns the amount of material in the composite state $\mathcal{c}$ that is prepared in the particle state $\mathcal{s}$. For example, given a certain configuration of gas, we can tell the density of material that is at a specific point in space with a specific value of momentum.

@@

On a state space with countable elements, using a single state variable, we have $\Lambda_U (\mathcal{c}) = \sum \limits_{q=a}^b \rho_\mathcal{c}(q)$. We would expect the expression to become $\Lambda_U (\mathcal{c}) = \int_a^b \rho_\mathcal{c} (q) dq$ for states identified by a continuous state variable. By changing state variable, though, we see that this does not work in general: $\rho_\mathcal{c}(\hat{q})= \rho(q)_\mathcal{c} dq/d\hat{q}$. This makes $\rho_\mathcal{c}$ a function not just of the state $\mathcal{s}$, but also of the state variables we are using. This is inconsistent with our previous definition. Moreover if the transformation is not differential, the density is not even well-defined. This tells us that $\mathcal{S}$ cannot be any manifold: it has to be one that allows state-variable-independent densities.

The first order of business is to guarantee that the density remains defined under an arbitrary change of state variables. This means the Jacobian of the transformation must exist. For the Jacobian to exist the transformation between state variables has to be differentiable. Therefore a manifold that guarantees densities to be well defined is one that guarantees that state variable transformations are differentiable: a differentiable manifold. $\mathcal{S}$ has a differentiable structure in the sense that the distributions and the volume element $d\mu$ are only defined on a set of state variables that are linked by differential transformations. In the same way that discontinuous changes of state variable can be detected because they tamper with physical distinguishability (i.e. the topology), non differentiable changes of state variable can be detected because they tamper with our ability to define state-variable-independent densities.

Moreover, the density itself has to be differentiable. The distribution $\rho_\mathcal{c}$ is a real valued function of the state. As such, at least locally, we can use it as a state variable $q^1=\rho_\mathcal{c}$: we can identify particle states by the density of the material associated with them. This is more physically meaningful than one may first suspect, since placing physical markers (i.e. placing material at particular states) is a common way to define the references for a coordinate system. In a coordinate system where $q^1=\rho_\mathcal{c}$, the function is clearly differential as $\partial_1 \rho_\mathcal{c} = 1$ and $\partial_i \rho_\mathcal{c} = 0$ for $i \neq 1$. As we change state variables, the transformation is differentiable, therefore all the derivatives $\partial_{i'} q^1 = \partial_{i'} \rho_\mathcal{c}$ exist. The density itself is differentiable.

\begin{prop}\label{prop:differentiable_manifold}
	The state space $\mathcal{S}$ for the particles of a  classical material is a differentiable manifold. The state space $\mathcal{C}$ for a classical material is isomorphic to the space of Lebesgue integrable differentiable functions. That is $\mathcal{C} \cong C^1(\mathcal{S}) \cap L^1(\mathcal{S}, \mu)$, where $C^1(\mathcal{S}) \equiv \{\rho:\mathcal{S} \rightarrow \mathbbm{R} \; | \; \rho$ is differentiable$\}$.
\end{prop}
\begin{justification}
	We claim $\mathcal{S}$ is a differential manifold. Let $\rho_\mathcal{c} : \mathcal{S} \rightarrow \mathbbm{R}$ be the distribution associated with a composite state $\mathcal{c} \in \mathcal{C}$. Let $q^i$ and $\hat{q}^j$ two sets of independent state variables in $U\subseteq \mathcal{S}$. Let $\rho_\mathcal{c}(q^i)$ and $\rho_\mathcal{c}(\hat{q}^j)$ be the expression in local coordinates of the distribution.  $\rho_\mathcal{c}(\hat{q}^j)=\rho_\mathcal{c}(q^i) | \partial_j q^i |$ as $\rho_\mathcal{c}$ transforms as a density. $\rho_\mathcal{c}(\mathcal{s}) = \rho_\mathcal{c}(q^i(\mathcal{s})) = \rho_\mathcal{c}(\hat{q}^j(\mathcal{s}))$. The Jacobian $| d q' / d q |$ exists and is non-zero. The map between any two charts is differentiable. $\mathcal{S}$ is a differentiable manifold.

@@

The cardinality of possibilities for each d.o.f. (i.e. the wedge product within a d.o.f.) and the orthogonality of different d.o.f. (i.e. the scalar product across d.o.f.) must be the same regardless of the choice of state variables. We can express both requirements mathematically in a compact way. We first define conjugate momentum as $p_i=\hbar k_i$ and unified state variables as $\xi^a\equiv \{q^i, p_i\}$. Then we consider the canonical two-form $\omega$ given by the following components:
\begin{align*}
\omega_{ab} =  \left[
\begin{array}{cc}
0 & 1 \\
-1 & 0 \\
\end{array}
\right] \otimes I_n =
\left[
\begin{array}{cc}
0 & I_n \\
-I_n & 0 \\
\end{array}
\right] \\
\end{align*}
It returns the wedge product within a d.o.f. and the scalar product across. Requiring the invariance of this metric under state variable changes assures us the cardinality of states and possibilities is well defined.

This gives us insight on the physical meaning of the geometrical structure $T^*\mathcal{Q}$. The canonical one-form $\theta=k dq$ represents the geometrical object we associate with each particle state. The canonical two-form $\omega=\Sigma \, dq^i \wedge dp_i$ is the metric that quantifies the possibilities described by two given state variables. Note, instead, that the relationship $\omega = - \hbar d\theta$, while mathematically true, has no clear physical meaning as we have not defined what the exterior derivative on a state actually represents.

@@

\begin{justification}
	We claim the simplest state space $\mathcal{S}$ that allows state-variable-invariant densities is the cotangent bundle $T^*\mathcal{Q}$ of a single dimensional manifold $\mathcal{Q}$. Consider a set of state variables for $U \in \mathcal{S}$: the simplest unit system is one defined by a single state variable. Let $q$ be the state variable that defines the unit system. Let $\mathcal{Q}$ be the manifold charted by $q$. A diffeomorphism $\hat{q}=\hat{q}(q)$ fully defines a unit transformation. Let $(q,k^i)$ with $i=1...n-1$ be a set of state variables. The Jacobian determinant $|J| = d_q\hat{q} |\partial_i\hat{k}^j|=1$ as densities must be invariant. $|\partial_i \hat{k}^j| = d_{\hat{q}}q$. $\partial_i \hat{k}^j$ is one dimensional as its components must be fully specified by the previous relationship. Let $k=k^1$. $\partial_k \hat{k} = d_{\hat{q}}q$. $\hat{k}(q,0) = 0$ as a change in units does not change the $0$ value. $\hat{k} = d_{\hat{q}}q k$. $k$ changes as the component of a co-vector. Each state is identified by a point and a co-vector in $\mathcal{Q}$. The simplest state space $\mathcal{S}$ is isomorphic to $T^*\mathcal{Q}$ where $Q$ is the one dimensional manifold that defines the units.

	We claim the simplest state space $\mathcal{S}$ that allows state-variable-invariant densities is the symplectic manifold $(T^*\mathcal{Q}, \omega)$ where $T^*\mathcal{Q}$ is the cotangent bundle of a one dimensional differential manifold $\mathcal{Q}$ and $\omega$ is the canonical two-form. Express integration in coordinates. $\int_{\mathcal{S}} \rho_\mathcal{c} d\mu \propto \int_{\mathcal{S}} \rho_\mathcal{c}(q, k) dq \wedge dk$. $d\mu = \hbar dq \wedge dk = dq \wedge dp = \omega$ where $\hbar$ is a constant, $p\equiv \hbar k$  and $\omega$ is the canonical two form. $\omega$ is invariant under state variable change. $\omega$ is a symplectic metric for $\mathcal{S}=T^*\mathcal{Q}$. $\mathcal{S} = (T^*\mathcal{Q}, \omega)$ is a symplectic manifold.

	We claim the state space $\mathcal{S}$ for the particles of a homogeneous classical material is a symplectic manifold $(T^*\mathcal{Q}, \omega)$ where $T^*\mathcal{Q}$ is the cotangent bundle of an $n$-dimensional differential manifold $\mathcal{Q}$ and $\omega$ is the canonical two-form. Let $q^i$ be a set of n continuous independent state variables that define the units necessary to describe a state in $U \subseteq \mathcal{S}$. Let $\mathcal{Q}$ be the manifold charted by $q^i$. Locally $\mathcal{Q} \cong \prod \mathcal{Q}^i \cong \mathbbm{R}^n$. Changing units of one state variable must not change the units of the other as they are independent. State-variable-distribution can  be defined separately on each degree of freedom. For each $\mathcal{Q}^i$ we have a covector $k_i(q) dq^i \in T^*\mathcal{Q}^i$. Locally $\mathcal{S} \cong \prod T^*\mathcal{Q}^i \cong T^* \prod \mathcal{Q}^i \cong T^* \mathcal{Q}$. Integration must also be defined on an independent d.o.f. There must exist a non-degenerate two-form $\omega$ such that $\int_{U \subset \mathcal{S}} \rho_\mathcal{c} \omega$ where $U$ is any two dimensional surface in $\mathcal{S}$. $\omega$ has to be form invariant under state variable change. The canonical two-form is the only such form. $\omega = \sum dq^i \wedge dp_i$. $\mathcal{S} = (T^*\mathcal{Q}, \omega)$ is a symplectic manifold.
\end{justification}

@@

\begin{justification}
	We claim the space of physical objects that allows time-and-state-variable-invariant densities is a symplectic manifold $(T^*\mathcal{M}, \omega)$ where $\omega = \sum dq^i \wedge dp_i - dt \wedge dE$. Let $\mathcal{M}$ be the manifold that defines the unit system including time. Locally $\mathcal{M} \cong \mathcal{Q} \times \mathbbm{R}$ as time and state variables are independent quantities. As in \ref{symplectic_manifold}, invariant densities are defined on the symplectic manifold $(T^*\mathcal{M}, \omega)$. Let $\bar{\omega}$ be the co-vector component associated with $t$. Let $E\equiv\hbar \bar{\omega}$. Let $\omega$ be the metric. The components of $\omega$ across different d.o.f. must be zero as they are not invariant under unit transformations. $\omega=\sum dq^i \wedge dp_i \pm dt \wedge dE$. The $+$ case is excluded as the temporal degree is not an independent d.o.f.: $\omega = \sum dq^i \wedge dp_i - dt \wedge dE$.

@@

	We claim $(x^\alpha, u^\alpha) \mapsto (q^\alpha, p_\alpha)$ is a diffeomorphism. Let $\bar{\mathcal{c}}$ be the evolution of a minimal classical material. Let $\rho_{\bar{\mathcal{c}}} : \bar{\mathcal{S}} \rightarrow \mathbbm{R}$ be the distribution associated with $\bar{\mathcal{c}}$. $\rho_{\bar{\mathcal{c}}}(\mathcal{s}(x^\alpha, u^\alpha))$ as the material is minimal. $\rho_{\bar{\mathcal{c}}}(x^\alpha, u^\alpha)$ is differential by the same logic expressed in \ref{prop:differentiable_manifold}. $(x^\alpha, u^\alpha) \mapsto (q^\alpha, p_\alpha)$ is a diffeomorphism as it as a homeomorphism that maps a differentiable function to a differentiable function.
\end{justification}

>>>>

We claim $\mathcal{T}_{\Delta t}$ is continuous. Let $U \subseteq \mathcal{S}$ represent an outcome of a process $P$ on the final states. $U$ is an open set in the (final) state space topology by definition. Consider the process $P_0$ that first evolves the initial states and then distinguishes the final state with $P$. $P_0$ is a process that distinguishes initial states. The set of initial states compatible with $U$ are $\mathcal{T}_{\Delta t}^{-1}(U)$. $\mathcal{T}_{\Delta t}^{-1}(U)$ is an open set in the (initial) state space topology by definition. $\mathcal{T}_{\Delta t}$ is a continuous map.

@@

\begin{justification}
	Same justification for continuity as in \ref{detrevmap} with ``initial states" and ``final states" replaced by "elements" of $\mathcal{S_1}$ and $\mathcal{S_2}$ respectively.
\end{justification}

@@

When combining multiple state variables, it is important to understand how they relate to each other. Consider the orbital of an electron in a hydrogen atom, which is identified by the quantum numbers $n$, $l$, $m$ and $s$. For each combination of $n$, $l$ and $m$, the spin $s$ can have two values. The choice of spin is independent from the rest. The choice of $l$, though, depends on the choice of $n$: for $n=1$ only $l=0$ is available; for $n=2$ we can choose $l=0$ or $l=1$. The choices are not independent. That is: two or more variables are independent if there always exists a state for any possible combination, if the total number of states is the cartesian product of the possibilities of each variable. We call \emph{state vector} a collection of independent state variables that fully identify a state.

\begin{prop}\label{independent_state_variables}
	Two state variables $q_1 : U \rightarrow \mathbbm{L}_1$ and $q_2 : U \rightarrow \mathbbm{L}_2$ are said \emph{independent} if $\exists \mathcal{s}$ such that $q_1(\mathcal{s})=l_1, q_2(\mathcal{s})=l_2 \forall l_1 \in q_1(U), l_2 \in q_2(U)$.
\end{prop}

@@

We will call a \emph{classical material} one that is homogeneous and infinitesimally reducible. That is, we can keep decomposing the system indefinitely into smaller and smaller parts, each with a well defined state. In this case, the particles are the infinitesimal parts given by the limit of this process of recursive decomposition. Giving the state of the whole system is equivalent to giving the states of all particles. Given the state space $\mathcal{S}$ for the infinitesimal parts, which we assume consistently with \ref{continuous_state_space} to be a manifold, a composite state $\mathcal{c} \in \mathcal{C}$ will tell us the amount of material for each possible particle state. That is, each state is fully identified by a function $\rho_\mathcal{c}: \mathcal{S} \to \mathbbm{R}$ that returns the amount of material in the composite state $\mathcal{c}$ that is prepared in the particle state $\mathcal{s}$. For example, given a certain configuration of gas, we can tell the density of material that is at a specific point in space with a specific value of momentum.

@@

On a state space with countable elements, using a single state variable, we have $\Lambda_U (\mathcal{c}) = \sum \limits_{q=a}^b \rho_\mathcal{c}(q)$. We would expect the expression to become $\Lambda_U (\mathcal{c}) = \int_a^b \rho_\mathcal{c} (q) dq$ for states identified by a continuous state variable. By changing state variable, though, we see that this does not work in general: $\rho_\mathcal{c}(\hat{q})= \rho(q)_\mathcal{c} dq/d\hat{q}$. This makes $\rho_\mathcal{c}$ a function not just of the state $\mathcal{s}$, but also of the state variables we are using. This is inconsistent with our previous definition. Moreover if the transformation is not differentiable, the density is not even well-defined. This tells us that $\mathcal{S}$ cannot be any manifold: it has to be one that allows state-variable-independent densities.

The first order of business is to guarantee that the density remains defined under an arbitrary change of state variables. This means the Jacobian of the transformation must exist. For the Jacobian to exist the transformation between state variables has to be differentiable. Therefore a manifold that guarantees densities to be well defined is one that guarantees that state variable transformations are differentiable: a differentiable manifold. $\mathcal{S}$ has a differential structure in the sense that the distributions and the volume element $d\mu$ are only defined on a set of state variables that are linked by differentiable transformations. In the same way that discontinuous changes of state variable can be detected because they tamper with physical distinguishability (i.e. the topology), non differentiable changes of state variable can be detected because they tamper with our ability to define state-variable-independent densities.

Moreover, the density itself has to be differentiable. The distribution $\rho_\mathcal{c}$ is a real valued function of the state. As such, at least locally, we can use it as a state variable $q^1=\rho_\mathcal{c}$: we can identify particle states by the density of the material associated with them. This is more physically meaningful than one may first suspect, since placing physical markers (i.e. placing material at particular states) is a common way to define the references for a coordinate system. In a coordinate system where $q^1=\rho_\mathcal{c}$, the function is clearly differentiable as $\partial_1 \rho_\mathcal{c} = 1$ and $\partial_i \rho_\mathcal{c} = 0$ for $i \neq 1$. As we change state variables, the transformation is differentiable, therefore all the derivatives $\partial_{i'} q^1 = \partial_{i'} \rho_\mathcal{c}$ exist. The density itself is differentiable.

\begin{prop}\label{prop:differentiable_manifold}
	The state space $\mathcal{S}$ for the particles of a  classical material is a differentiable manifold. The state space $\mathcal{C}$ for a classical material is isomorphic to the space of Lebesgue integrable differentiable functions. That is $\mathcal{C} \cong C^1(\mathcal{S}) \cap L^1(\mathcal{S}, \mu)$, where $C^1(\mathcal{S}) \equiv \{\rho:\mathcal{S} \rightarrow \mathbbm{R} \; | \; \rho$ is differentiable$\}$.
\end{prop}
\begin{justification}
	We claim $\mathcal{S}$ is a differentiable manifold. Let $\rho_\mathcal{c} : \mathcal{S} \rightarrow \mathbbm{R}$ be the distribution associated with a composite state $\mathcal{c} \in \mathcal{C}$. Let $q^i$ and $\hat{q}^j$ two sets of independent state variables in $U\subseteq \mathcal{S}$. Let $\rho_\mathcal{c}(q^i)$ and $\rho_\mathcal{c}(\hat{q}^j)$ be the expression in local coordinates of the distribution.  $\rho_\mathcal{c}(\hat{q}^j)=\rho_\mathcal{c}(q^i) | \partial_j q^i |$ as $\rho_\mathcal{c}$ transforms as a density. $\rho_\mathcal{c}(\mathcal{s}) = \rho_\mathcal{c}(q^i(\mathcal{s})) = \rho_\mathcal{c}(\hat{q}^j(\mathcal{s}))$. The Jacobian $| d q' / d q |$ exists and is non-zero. The map between any two charts is differentiable. $\mathcal{S}$ is a differentiable manifold.

@@

The cardinality of possibilities for each d.o.f. (i.e. the wedge product within a d.o.f.) and the orthogonality of different d.o.f. (i.e. the scalar product across d.o.f.) must be the same regardless of the choice of state variables. We can express both requirements mathematically in a compact way. We first define conjugate momentum as $p_i=\hbar k_i$ and unified state variables as $\xi^a\equiv \{q^i, p_i\}$. Then we consider the canonical two-form $\omega =\Sigma \, dq^i \wedge dp_i$ given by the following components:
\begin{align*}
\omega_{ab} =  \left[
\begin{array}{cc}
0 & 1 \\
-1 & 0 \\
\end{array}
\right] \otimes I_n =
\left[
\begin{array}{cc}
0 & I_n \\
-I_n & 0 \\
\end{array}
\right] \\
\end{align*}
It returns the wedge product within a d.o.f. and the scalar product across. Requiring the invariance of this metric under state variable changes assures us the cardinality of states and possibilities is well defined.

This gives us insight on the physical meaning of the geometrical structure $T^*\mathcal{Q}$. The canonical one-form $\theta=k dq$ represents the geometrical object we associate with each particle state. The canonical two-form $\omega$ is the metric that quantifies the possibilities described by two given state variables. Note, instead, that the relationship $\omega = - \hbar d\theta$, while mathematically true, has no clear physical meaning as we have not defined what the exterior derivative on a state actually represents.

@@

\begin{justification}
	We claim the simplest state space $\mathcal{S}$ that allows state-variable-invariant densities is the cotangent bundle $T^*\mathcal{Q}$ of a single dimensional manifold $\mathcal{Q}$. Consider a set of state variables for $U \in \mathcal{S}$: the simplest unit system is one defined by a single state variable. Let $q$ be the state variable that defines the unit system. Let $\mathcal{Q}$ be the manifold charted by $q$. A diffeomorphism $\hat{q}=\hat{q}(q)$ fully defines a change of units. Let $(q,k^i)$ with $i=1...n-1$ be a set of state variables. The Jacobian determinant $|J| = d_q\hat{q} |\partial_i\hat{k}^j|=1$ as densities must be invariant. $|\partial_i \hat{k}^j| = d_{\hat{q}}q$. $\partial_i \hat{k}^j$ is one dimensional as its components must be fully specified by the previous relationship. Let $k=k^1$. $\partial_k \hat{k} = d_{\hat{q}}q$. $\hat{k}(q,0) = 0$ as a change in units does not change the $0$ value. $\hat{k} = d_{\hat{q}}q k$. $k$ changes as the component of a co-vector. Each state is identified by a point and a co-vector in $\mathcal{Q}$. The simplest state space $\mathcal{S}$ is isomorphic to $T^*\mathcal{Q}$ where $Q$ is the one dimensional manifold that defines the units.

	We claim the simplest state space $\mathcal{S}$ that allows state-variable-invariant densities is the symplectic manifold $(T^*\mathcal{Q}, \omega)$ where $T^*\mathcal{Q}$ is the cotangent bundle of a one dimensional differentiable manifold $\mathcal{Q}$ and $\omega$ is the canonical two-form. Express integration in coordinates. $\int_{\mathcal{S}} \rho_\mathcal{c} d\mu \propto \int_{\mathcal{S}} \rho_\mathcal{c}(q, k) dq \wedge dk$. $d\mu = \hbar dq \wedge dk = dq \wedge dp = \omega$ where $\hbar$ is a constant, $p\equiv \hbar k$  and $\omega$ is the canonical two form. $\omega$ is invariant under state variable change. $\omega$ is a symplectic metric for $\mathcal{S}=T^*\mathcal{Q}$. $\mathcal{S} = (T^*\mathcal{Q}, \omega)$ is a symplectic manifold.

	We claim the state space $\mathcal{S}$ for the particles of a homogeneous classical material is a symplectic manifold $(T^*\mathcal{Q}, \omega)$ where $T^*\mathcal{Q}$ is the cotangent bundle of an $n$-dimensional differentiable manifold $\mathcal{Q}$ and $\omega$ is the canonical two-form. Let $q^i$ be a set of n continuous independent state variables that define the units necessary to describe a state in $U \subseteq \mathcal{S}$. Let $\mathcal{Q}$ be the manifold charted by $q^i$. Locally $\mathcal{Q} \cong \prod \mathcal{Q}^i \cong \mathbbm{R}^n$. Changing units of one state variable must not change the units of the other as they are independent. State-variable-distribution can  be defined separately on each degree of freedom. For each $\mathcal{Q}^i$ we have a covector $k_i(q) dq^i \in T^*\mathcal{Q}^i$. Locally $\mathcal{S} \cong \prod T^*\mathcal{Q}^i \cong T^* \prod \mathcal{Q}^i \cong T^* \mathcal{Q}$. Integration must also be defined on an independent d.o.f. There must exist a non-degenerate two-form $\omega$ such that $\int_{U \subset \mathcal{S}} \rho_\mathcal{c} \omega$ where $U$ is any two dimensional surface in $\mathcal{S}$. $\omega$ has to be form invariant under state variable change. The canonical two-form is the only such form. $\omega = \sum dq^i \wedge dp_i$. $\mathcal{S} = (T^*\mathcal{Q}, \omega)$ is a symplectic manifold.
\end{justification}

@@

\begin{justification}
	We claim the space of physical objects that allows time-and-state-variable-invariant densities is a symplectic manifold $(T^*\mathcal{M}, \omega)$ where $\omega = \sum dq^i \wedge dp_i - dt \wedge dE$. Let $\mathcal{M}$ be the manifold that defines the unit system including time. Locally $\mathcal{M} \cong \mathcal{Q} \times \mathbbm{R}$ as time and state variables are independent quantities. As in \ref{symplectic_manifold}, invariant densities are defined on the symplectic manifold $(T^*\mathcal{M}, \omega)$. Let $\bar{\omega}$ be the co-vector component associated with $t$. Let $E\equiv\hbar \bar{\omega}$. Let $\omega$ be the metric. The components of $\omega$ across different d.o.f. must be zero as they are not invariant under change of units. $\omega=\sum dq^i \wedge dp_i \pm dt \wedge dE$. The $+$ case is excluded as the temporal degree is not an independent d.o.f.: $\omega = \sum dq^i \wedge dp_i - dt \wedge dE$.

@@

	We claim $(x^\alpha, u^\alpha) \mapsto (q^\alpha, p_\alpha)$ is a diffeomorphism. Let $\bar{\mathcal{c}}$ be the evolution of a minimal classical material. Let $\rho_{\bar{\mathcal{c}}} : \bar{\mathcal{S}} \rightarrow \mathbbm{R}$ be the distribution associated with $\bar{\mathcal{c}}$. $\rho_{\bar{\mathcal{c}}}(\mathcal{s}(x^\alpha, u^\alpha))$ as the material is minimal. $\rho_{\bar{\mathcal{c}}}(x^\alpha, u^\alpha)$ is differentiable by the same logic expressed in \ref{prop:differentiable_manifold}. $(x^\alpha, u^\alpha) \mapsto (q^\alpha, p_\alpha)$ is a diffeomorphism as it as a homeomorphism that maps a differentiable function to a differentiable function.
\end{justification}
